\section{Current State of the Art}

A few trends are driving Video Game development across the industry. First, opportunities to monetize Video Gaming both for developers and
players are driving the development of certain types of games~\cite{b5}. On the Player side, monetization is led primarily by E-Sports and streaming. Because
of the recent spike in viewership for both E-Sport competition as well as streaming, many large AAA game developers are working on online,
multiplayer, competitive games, to try and get a part of the huge player base and viewership that games like \textit{Fortnite} have succeeded in
achieving. On the developer side, these types of games are set up well to provide microtransactions, or in-game purchases, for players who
are willing to spend additional money on top of game purchases to have unique characterization in massive online communities~\cite{b6}.

Other recent trends include the growth of massive, open world games, where the in-game map buffers naturally to give the Player the feeling that
there are endless opportunities for exploration and adventure~\cite{b7}. Growth in this area is fed by the critical success of games like \textit{Skyrim} or \textit{The
Legend of Zelda, Breath of the Wild}. These types of games have been made possible by huge advances in game engine technology, with engines like
Unity and Unreal making it possible to track thousands of assets, quickly load new scenes, and optimize game performance to allow for much
larger games than were previously possible.

The game concept proposed here does not follow these trends, but combines a few other popular game styles, Roguelike and Party Games. Roguelike
games are increasing in popularity, with a few large success stories in recent years. Two recent examples are \textit{Hollow Knight} and
\textit{Hades}, which both won multiple awards in their release year and achieved large player bases. Additionally, Party Games have been popular
for many years; for example, \textit{Mario Kart 8} is the sixth-best selling game of all time, with over 80 million copies sold. Combining these
genres with local-multiplayer, which is not available in many modern multiplayer games after the growth of internet-enabled games, positions this
concept to be unique in the market.
